\documentclass[a4paper, notitlepage]{article}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{9251}{\openboxtest}
\begin{document}

\title{TI2320 Theory of Computation, assignment 1 (tm-n-22)} 
\author{Zmitser Zhaleznichenka (\#4134575, group 39)}
\date{\today}
\maketitle

\setcounter{secnumdepth}{0}

\section{High-level description}

To decide on the given language $L$, we need a multi-tape Turing machine with two tapes having tape alphabet $\Gamma = \{0, 1, \#, *, ␣\}$. This Turing machine should operate as follows. 

\begin{enumerate}

\item Scan input for \#. If it is not found, or more than one is found, \emph{reject} (trivial).

\item Copy input from tape 1 to tape 2 (trivial).

\item At tape 1 compare \(\#_0\) and \(\#_1\) in x. To do this, for each 1 twice scan the string for 0 and replace these 0s with *, then replace 1 with *. After reaching \# check whether there are remaining 0s and 1s and \emph{reject} if so, proceed otherwise.

\item At tape 2 compare $x$ and $y^s$. Start from \# and zig-zag from it in both directions comparing the symbols under the head. If at any of the steps the symbols don't match, \emph{reject}. Otherwise, when two matching spaces found, \emph{accept}.

\end{enumerate}

\section{Implementation description}

\subsection{Comparing $\#_0$ and $\#_1$ in x}

\begin{enumerate}

\item Repeat steps 2-5 until you reach \# at any step.

\item Start from the beginning of the string and go from left to right upon reaching first 1.

\item Get back to the beginning and scan the string from left to right for first 0. Replace 0 with *.

\item Repeat steps 1-2 once.

\item Replace leftmost 1 with *.

\item Upon reaching \#, move left from this symbol and scan the string for 0 or 1. If you have found any of them, \emph{reject}. Otherwise, if the beginning of string reached, go to the following part.
\end{enumerate}

\subsection{Comparing $x$ and $y^s$}

\begin{enumerate}

\item Place the head at \# sign.

\item Move left until reaching any of \{0,1,␣\} and replace it with \#.

\item Move right until reaching first non-\# symbol.

\item If it equals the replaced symbol and both symbols are spaces, \emph{accept}. Otherwise, if the symbols are 0s or 1s, replace the symbol at head with \# and repeat steps 2-4. If symbols differ, \emph{reject}.

\end{enumerate}

\end{document}